Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-07 manuscript/manuscript.tex
more Gs changes

\subsubsection{Truncation Selection.}
\gc{We explored how directional truncation selection generated
  temporal covariances.In these simulations we select the top ${\bf X
    \%}$ of the phenotypic distribution of individuals to form the
  next generation. We burnin these simulations {\bf by
    XXXX}. More extreme directional truncation selection generated
  larger initial covariances (Figure
  \ref{suppfig:supp-trunc}B). However, weaker truncation selection
  generated more sustained positive covariances and so had a larger
  long term impact

@@

Through simulations, we noticed the strongest effect fixation  or loss of sites
has on temporal covariance and $G(t)$ is under truncation selection. Here,
since only a (potentially small) fraction of individuals contribute to the next
generation, sites can fix over very short timescales. Furthermore, the small
number of effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0$, the denominator of $G(t)$. We
see the effect of handling fixed/lost sites differently, and the faster rate of
drift in Supplementary Materials Figure \ref{suppfig:supp-trunc} (A), where
weaker truncation selection actually has higher levels of $G(t)$. Looking just
at temporal covariances, we find that stronger truncation selection (e.g.  a
smaller tail of individuals selected) does lead to greater temporal
covariances.

>>>>

\subsubsection{Truncation Selection.}
\gc{We explored how directional truncation selection generated
  temporal covariances.In these simulations we select the top ${\bf X
    \%}$ of the phenotypic distribution of individuals to form the
  next generation. We burnin these simulations {\bf by
    XXXX}. More extreme directional truncation selection generated
  larger initial covariances (Figure
  \ref{suppfig:supp-trunc}B). However, weaker truncation selection
  generated more sustained positive covariances and so had a larger
  long term overall impact on the variance in allele frequency change. 
\gc{We noticed again  strong effect fixation  or loss of sites
has on temporal covariance and $G(t)$ under truncation selection.}  Here,
since only a (potentially small) fraction of individuals contribute to the next
generation, sites can fix over very short timescales. Furthermore, the small
number of effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0$, the denominator of $G(t)$. We
see the effect of handling fixed/lost sites differently, and the faster rate of
drift in Supplementary Materials Figure \ref{suppfig:supp-trunc} (A), where
weaker truncation selection actually has higher levels of $G(t)$. Looking just
at temporal covariances, we find that stronger truncation selection (e.g.  a
smaller tail of individuals selected) does lead to greater temporal
covariances.

@@
